---
title: "LoadRecords"
output:
  pdf_document: default
  html_document: default
date: '2022-02-25'
---

## Introduction

This is a R Markdown document that quickly processes library items with errors at the UCSD Geisel Library. The goal of this project is to efficiently rearrange the necessary spreadsheets & save them in a single file. 

Project & file system setup are outlined in the ReadMe document within the library-test Github repository. If you have successfully cloned the Github repository & set up the file system in the ReadMe, then you are ready to use this document. 

### Step 1: load libraries

We load the R libraries that contain the functions we need to successfully process the spreadsheets. If you have not installed these libraries on your local computer before, you will need to use install.packages("PackageName") in the R console to install each library. Once installed, we use library(PackageName) to load the library into your R session in the code chunk below. Remember: **install once, load library for each time you start R.** 

To run the code chunk, hit the green arrow pointing right.


```{r loadlibraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(readxl)
library(writexl)

```

### Step 2: load spreadsheets & select columns

This step consists of 2 parts: **A.** listing the file path to all files that start with #2, #3, etc. and **B.** loading each group of files, binding them, and adding a Section column based on the file name the corresponding row was loaded from.

**IMPORTANT:** Each time you run the script, make sure that here() is calling to the correct folder name, e.g., the correct Range. This means double-checking the Range/folder name within here() for each list. Otherwise, you might load the wrong set of files.

If there are no files present for a particular list, the list will say "character (empty)" in the R environment. As a result, R will throw an "Error: Can't subset columns that don't exist." when a group attempts to be made from an empty list. That is okay -- just move on and run the next group. Alternatively, you can only run the groups for which the corresponding list is not empty. 

```{r loadspreadsheets}

list2 <- list.files(path = here("rawdata", "Range38B"), pattern = "#2", full.names = TRUE)
list3 <- list.files(path = here("rawdata", "Range38B"), pattern = "#3", full.names = TRUE)
list5 <- list.files(path = here("rawdata", "Range38B"), pattern = "#5", full.names = TRUE)
list6 <- list.files(path = here("rawdata", "Range38B"), pattern = "#6", full.names = TRUE)

group2 <- list2 %>%
  set_names() %>% 
  map_dfr(read_excel, .id = "source") %>%
  mutate(Section = substr(sub(".*Section", "", source), 1, 2))
group3 <- list3 %>%
  set_names() %>% 
  map_dfr(read_excel, .id = "source") %>%
  mutate(Section = substr(sub(".*Section", "", source), 1, 2))
group5 <- list5 %>%
  set_names() %>% 
  map_dfr(read_excel, .id = "source") %>%
  mutate(Section = substr(sub(".*Section", "", source), 1, 2))
group6 <- list6 %>%
  set_names() %>% 
  map_dfr(read_excel, .id = "source") %>%
  mutate(Section = substr(sub(".*Section", "", source), 1, 2))

```

### Step 3: select columns

This step selects the columns for each group of files and puts them in the order listed in the code. 

The code will throw an "Error: Can't subset columns that don't exist." for groups with 0 obs in the R environment. That's okay, just move on and run the next group. Alternatively, you can only run the groups for which observations are available.

```{r selectcolumns, echo=FALSE}
group2 <- dplyr::select(group2, "Call Number", "Copy ID", Description, Title, Barcode, "Permanent Location", Section)
group3 <- dplyr::select(group3, "Call Number", "Copy ID", Description, Title, Barcode, "Modification Date", "Process type", "Permanent Location", Section)
group5 <- dplyr::select(group5, "Call Number", "Copy ID", Description, Title, Barcode, "Permanent Location", Section)
group6 <- dplyr::select(group6, Barcodes, Section)
```



### Step 4: sort spreadsheets

We can set a rule for how to sort the spreadsheets. 

```{r sortspreadsheets, echo=FALSE}

```

### Step 5: save spreadsheets

The write_xlsx function below makes each group a separate sheet in a new .xlsx file. Make sure to:

1. Change the Range in the .xlsx file name to match the range in the file folder name you are working in (see Step 2 to confirm the Range you already selected)
2. Only include groups in the list() that have observations in the R environment. e.g., if you were unable to make group5 in step 2 above, you would need to remove group5 from the code below.

```{r savespreadsheets, echo=FALSE}
write_xlsx(list(group2, group3, group5, group6), here("outputs", "CompiledRecords_Range38B.xlsx"))
```